Similar Sentence Detection Using Locality Sensitive Hashing Technique on Wikipedia

### 2013-11-12 article/article-draft.tex
Fixed conf for minimum similarity argument in sentence similarity code. Added argument to toggle filtering.

 For clarity purposes, we define \emph{similarity count} as simply the total number of unique sentences between two articles that were found to share the same hash signature. Using the output of the minhashing routine, we performed a pairwise similarity count across all articles that shared similar sentences to identify the articles that are most similar by this measure. Overall, we found $\approx 121000$ wikipedia article paris that had a similarity count greater than or equal to $20$ and $\approx 29580$ wikipedia article pairs that had a similarity count greater than or equal to $50$.

>>>>

 For clarity purposes, we define \emph{similarity count} as simply the total number of unique sentences between two articles that were found to share the same hash signature. Using the output of the minhashing routine, we performed a pairwise similarity count across all articles that shared similar sentences to identify the articles that are most similar by this measure. Overall, we found $\approx 121,000$ wikipedia article paris that had a similarity count greater than or equal to $20$ and $\approx 29,580$ wikipedia article pairs that had a similarity count greater than or equal to $50$. If we performt the same similarity analysis, but filter clusters using the template heuristic described above,
